---
title: "Continuous_spatial"
author: "GauthierGad"
date: "2023-10-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Interpolation of the discrete data into map of continuous data. Use of Voronoi triangles. We convert a set of observations of a field at discrete positions
into a surface.

```{r}
library(deldir)
library(isdas)
library(plotly)
library(spatstat)
library(spdep)
library(tidyverse)
library(readxl)
library(gstat)
library(stars)
```

```{r}
rm(list = ls())
path <- "/Users/gauthier.gadouas/Desktop/Projet AFM/Data/Original_data"

# Initialize lists to store file paths and filenames
file_paths <- character(0)
file_names <- character(0)

# Recursively find Excel files with "map" in their name
excel_files <- list.files(path, pattern = ".*map.*\\.xlsx$", full.names = TRUE, recursive = TRUE)

# Iterate over the Excel files and gather paths and filenames
for (path_to_file in excel_files) {
  file_paths <- c(file_paths, path_to_file)
  file_names <- c(file_names, basename(path_to_file))
}
```

```{r}
data <- read_excel(file_paths[77])
subset_data <- data %>%
    mutate(`X Position` = as.numeric(`X Position`),
           `Y Position` = as.numeric(`Y Position`),
           `Young's Modulus [Pa]`= as.numeric(`Young's Modulus [Pa]`))
```

```{r}
# Convert numeric_df to an sf object
coordinates <- subset_data[, c("X Position", "Y Position")]
sf_object <- st_as_sf(coordinates, coords = c("X Position", "Y Position"))
sf_object <- matrix(st_coordinates(sf_object), ncol=2)
sf_object <- st_multipoint(sf_object, dim = "XY")

box = st_polygon(list(rbind(c(-3e-5,-3e-5),c(3e-5,-3e-5),c(3e-5, 3e-5),c(-3e-5,3e-5),c(-3e-5,-3e-5))))

# Create a plot of the coordinates and the window
p <- ggplot(data = subset_data) + 
  geom_sf(data = sf_object, size = 2) +
  geom_sf(data = box, 
          fill = NA)

# Create a triangulation that connect each point to its two 
# nearest neighbors.

l2n <- st_triangulate(sf_object, bOnlyEdges = TRUE)

# Plot the triangulation, i.e., the lines between nearest neighbors
ggplot(data = subset_data) + 
  geom_sf(data = sf_object, size = 2) +
  geom_sf(data = box, 
          fill = NA) +
  geom_sf(data = l2n, 
          color = "gray", 
          linetype = "dashed")

# create Voronoi polygons based on points
vor <- st_voronoi(sf_object) 

vpolygons <- do.call(c, st_geometry(sf_object)) %>%
  st_voronoi() %>%
  st_collection_extract()

ggplot(vpolygons) +
  geom_sf(fill=NA) + 
  coord_sf(xlim = c(-3e-5, 3e-5), ylim = c(-3e-5, 3e-5))

Young_modulus.v <- sf_object
Young_modulus.v$geometry.<- vpolygons[unlist(st_intersects(sf_object, vpolygons))]

#ggplot(data = subset_data) +
#  geom_sf(size = 2) + 
#  geom_sf(data = l2n, 
#          color = "gray", 
#          linetype = "dashed") + 
#  geom_sf(data = vor, 
#          fill = NA) + 
#  coord_sf(xlim = c(-3e-5, 3e-5), 
#           y = c(-3e-5, 3e-5))
```

TEST N°2 POPOPOOOO

```{r}
map.sf <- subset_data %>%
  st_as_sf(coords = c("X Position", "Y Position"))

vpolygons <- do.call(c, st_geometry(map.sf)) %>% 
  st_voronoi() %>% 
  st_collection_extract()

triangulation <- ggplot(vpolygons)+
  geom_sf(fill = NA)
ggsave('triangulation.svg', triangulation)

map.v <- map.sf
map.v$geometry <- vpolygons[unlist(st_intersects(map.sf), vpolygons)]

#ggplot(map.v) + 
#  geom_sf(aes(fill = `Young's Modulus [Pa]`)) +
#  scale_fill_distiller(palette = "BuPu", 
#                       direction = 1)

m.bbox <- st_polygon(list(rbind(c(-3e-5,-3e-5),
                                c(-3e-5,3e-5),
                                c(3e-5, 3e-5),
                                c(3e-5, -3e-5),
                                c(-3e-5, -3e-5))))

map.v <- map.v %>%
  st_intersection(m.bbox)

voronoi_poly <- ggplot(map.v) + 
  geom_sf(aes(fill = `Young's Modulus [Pa]`)) + 
  geom_sf(data = map.sf,
          size = 0.1) +
  coord_sf(xlim = c(-3e-5, 3e-5), ylim = c(-3e-5, 3e-5)) +
  scale_fill_distiller(palette = "BuPu", 
                       direction = 1)

ggsave('voronoi_poly.svg', voronoi_poly)
```
Essayer avec le k-means ? We can have both the interpolated values as well as the local standard deviation. It is a crude estimator of the uncertainty because
at the end of the day, we do not know the underlying distribution.

```{r}
target_xy = expand.grid(x = seq(-3e-5, 3e-5, 5e-7), 
                        y = seq(-3e-5, 3e-5, 5e-7)) %>%
  st_as_sf(coords = c("x", "y"))

kpoint.3 <- kpointmean(source_xy = map.sf, 
                       target_xy = target_xy, 
                       z = `Young's Modulus [Pa]`,  
                       k = 3) %>%
  rename(`Young's Modulus [Pa]` = 2)

local_mean <- ggplot() +
  geom_sf(data = kpoint.3, 
          aes(color = `Young's Modulus [Pa]`)) +
  scale_color_distiller(palette = "BuPu", 
                       direction = 1)
ggsave("local_mean.svg", local_mean)

local_std <- ggplot() +
  geom_sf(data = kpoint.3, 
          aes(color = sd)) +
  scale_color_distiller(palette = "BuPu", 
                       direction = 1)
ggsave("local_std.svg", local_std)
```
On insère ensuite un bruit (on essaie de déterminer l'incertitude sur les interpolations effectuées) - SCD II

```{r}
ggplot(data=map.v, aes(`Young's Modulus [Pa]`)) +
         geom_histogram(binwidth = 100)
sd(map.v$`Young's Modulus [Pa]`)

```

One of the dowside of Voronoai polygons, or other methods as such, is that they accomplish the task of providinf spatial estimate. The random part of the estimate is left apart. The consequence is that is that
we cannot assess the uncertainty of the estimated values directly, which entirely depends on the distribution of the random term.

Trend surface analysis is a form of multivariate regression that fit a surface to the observation data. It is a method that permits to both obtain an estimate of the underlying field, AND a measure of the uncertainty of our predictions.
ATTENTION; it provides a confidence interval, so not an estimate of the prediction error. Just how confident we should be with the interpolation.
```{r}

trend_data <- mutate(subset_data, 
                     X3 = `X Position`^3, X2Y = `X Position`^2 * `Y Position`, X2 = `X Position`^2, 
                        XY = `X Position` * `Y Position`,
                        Y2 = `Y Position`^2, XY2 = `X Position` * `Y Position`^2, Y3 = `Y Position`^3,
                     Y = `Y Position`, X = `X Position`)

map.trend1 <- lm(formula = `Young's Modulus [Pa]` ~ X + Y, data = trend_data)
summary(map.trend1)
map.trend2 <- lm(formula = `Young's Modulus [Pa]` ~ X2 + Y2 + XY + X + Y, data = trend_data)
summary(map.trend2)
map.trend3 <- lm(formula = `Young's Modulus [Pa]` ~ X3 + Y3 + X2Y + X2 + X + XY + XY2 + Y2 + Y , data = trend_data)
summary(map.trend3)

X.p <- seq(from = -3e-5, to = 3e-5, by = 1e-6)
Y.p <- seq(from = -3e-5, to = 3e-5, by = 1e-6)
df.p <- expand.grid(X = X.p, Y = Y.p)

df.p <- mutate(df.p, X3 = X^3, X2Y = X^2 * Y, X2 = X^2, 
               XY = X * Y, 
               Y2 = Y^2, XY2 = X * Y^2, Y3 = Y^3)

#Compute predictions, upper bond and lower bond for confidence interval
map.preds3 <- predict(map.trend3, newdata = df.p, se.fit = TRUE, interval = "prediction", level = 0.95)
young.p3 <- matrix(data = map.preds3$fit[,1], nrow = 119, ncol = 103, byrow = TRUE)
young.p3_l <- matrix(data = map.preds3$fit[,2], nrow = 119, ncol = 103, byrow = TRUE)
young.p3_u <- matrix(data = map.preds3$fit[,3], nrow = 119, ncol = 103, byrow = TRUE)

map.plot3 <- plot_ly(x = ~X.p, y = ~Y.p, z = ~young.p3, 
        type = "surface", colors = "BuPu") %>% 
  add_surface(x = ~X.p, y = ~Y.p, z = ~young.p3_l, 
              opacity = 0.5, showscale = FALSE) %>%
  add_surface(x = ~X.p, y = ~Y.p, z = ~young.p3_u, 
              opacity = 0.5, showscale = FALSE) %>% 
  layout(scene = list(
    aspectmode = "manual", aspectratio = list(x = 1, y = 1, z = 1)))
map.plot3
map.plot3 %>%
  add_markers(data = subset_data, x = ~ `X Position`, y = ~`Y Position`, z = ~`Young's Modulus [Pa]`, 
              color = ~`Young's Modulus [Pa]`, opacity = 0.7, showlegend = FALSE)
```

The method is not so good with the point estimate. Failed to capture spatial variability ? ==> We plot positive or negative residuals

```{r}
data$residual3 <- ifelse(map.trend3$residuals > 0, "+", "-")
ggplot(data = data,
       aes(x=`X Position`, y=`Y Position`, color=residual3))+
  geom_point() +
  coord_equal()
```

The problem with this type of methods is that the residuals seem to be autocorrelated, i.e not independent. 
We are interested in exploring the properties of the pattern over the field, where the underlying process is typically smooth.
For that, we use VARIOGRAPHIC ANALYSIS.
We define autocovariance: it is the difference between a variable with itself at a different location. We need a criterio to define the spatial relationship between position i and j, ==> we need to predefine a spatial lag h. (Also, we consider that autocovariance is only a function of this position lag, i.e there is an isotropy of space).

```{r}
#Without using a model

names(map.sf)[names(map.sf) == "Young's Modulus [Pa]"] <- "YoungMod"
variogram_young <- gstat::variogram(YoungMod ~ 1, data = map.sf)

ggplot(data = variogram_young,
       aes(x = dist, 
           y = gamma)) + 
  geom_point() + 
  geom_text(aes(label = np), 
            nudge_y = -1500) +
  xlab("Distance") +
  ylab("Semivariance")

variogram_young.t <- fit.variogram(variogram_young, 
                               # Models to choosing the best fit
                               model = vgm("Exp", 
                                           "Sph", 
                                           "Gau",
                                           "Bes",
                                           "Ste")) 
variogram_young.t

gamma.t <- variogramLine(variogram_young.t, 
                         maxdist = 3.2e-5)

# Plot 
ggplot(data = variogram_young, 
       aes(x = dist, 
           y = gamma)) +
  geom_point(size = 3) + 
  geom_line(data = gamma.t,
            aes(x = dist, 
                y = gamma)) +
  xlab("Distance") + 
  ylab("Semivariance")
```

```{r}
plot_ly(x = ~data$`X Position`, 
        y = ~data$`Y Position`, 
        z = ~map.trend3$residuals, 
        color = ~map.trend3$residuals < 0, 
        colors = c("blue", "red"), 
        type = "scatter3d")

map.plot3 <- plot_ly(x = ~X.p, 
                    y = ~Y.p, 
                    z = ~young.p3, 
                    type = "surface", 
                    colors = "YlOrRd") %>% 
  layout(scene = list(aspectmode = "manual",
                      aspectratio = list(x = 1, 
                                         y = 1,
                                         z = 1)))
map.plot3

map.sf$residuals <- map.trend3$residuals

kpoint.5 <- kpointmean(source_xy = map.sf, 
                       target_xy = target_xy, 
                       z = residuals, 
                       k = 5)
z.p3 <- matrix(data = map.preds3$fit[,1] + kpoint.5$z,
               nrow = length(Y.p), 
               ncol = length(X.p), 
               byrow = TRUE)
map.plot3 <- plot_ly(x = ~X.p,
                     y = ~Y.p, 
                    z = ~z.p3,
                    type="surface",
                    colors="BuPu") %>%
  layout(scene = list(aspectmode="manual",
                      aspectratio=list( x = 1,
                                        y = 1,
                                        z = 1)))
map.plot3

```

We combined the interpolated residuals with the cubic trend surface. It provide a genuine estimate with trend surface analysis providing an estimator of the underlying field, and k-point means providing an estimator for the error or the uncertainty. But how to chose the right number of neighbours for calculating the k-pint means ? Furthermore, how to weight points in the spatial moving average according to distance ? 

```{r}

map.sf <- trend_data %>%
  st_as_sf(coords = c("X Position", "Y Position"))
names(map.sf)[names(map.sf) == "Young's Modulus [Pa]"] <- "YoungMod"

X.p <- seq(from = -2.6e-5, to = 2.6e-5, by = 1e-6)
Y.p <- seq(from = -2.6e-5, to = 2.6e-5, by = 1e-6)
df.p <- expand.grid(X = X.p, Y = Y.p)

df.p <- mutate(df.p, X2 = X^2, 
               XY = X * Y, 
               Y2 = Y^2)

df.sf <- df.p %>%
  st_as_sf(coords = c("X", "Y"),
           remove = FALSE)

variogram_young <- gstat::variogram( YoungMod ~  X2 + X + XY + Y + Y2,
                             data = map.sf)

ggplot(data = variogram_young, 
       aes(x = dist, 
           y = gamma)) +
  geom_point() + 
  geom_text(aes(label = np), 
            # Nudge the labels away from the points
            nudge_y = -1500) +
  xlab("Distance") +
  ylab("Semivariance")

map.sf$e <- map.trend3$residuals
variogram_young.t <- fit.variogram(variogram_young, model = vgm("Exp", "Sph", "Gau"))
variogram_young.t

gamma.t <- variogramLine(variogram_young.t, maxdist = 5e-6)
ggplot(data = variogram_young,
       aes(x = dist, 
           y = gamma)) +
  geom_point(size = 3) + 
  geom_line(data = gamma.t,
            aes(x = dist, 
                y = gamma)) +
  xlab("Distance") + 
  ylab("Semivariance")

Young.kriged <- krige(YoungMod ~ X2 + X + XY + Y + Y2,
                  map.sf, 
                  df.sf, 
                  variogram_young.t)

Young.km <- matrix(data = Young.kriged$var1.pred,
               nrow = 50,
               ncol = 50, 
               byrow = TRUE)

Young.sm <- matrix(data = Young.kriged$var1.var,
               nrow = 50,
               ncol = 50, 
               byrow = TRUE)

Young.km.plot <- plot_ly(x = ~X.p,
                     y = ~Y.p, 
                     z = ~Young.km, 
                     type = "surface", 
                     colors = "YlOrRd") %>% 
  layout(scene = list(aspectmode = "manual", 
                      aspectratio = list(x = 1,
                                         y = 1,
                                         z = 1)))
Young.km.plot

Young.sm.plot <- plot_ly(x = ~X.p, 
                     y = ~Y.p,
                     z = ~sqrt(Young.sm), 
                     type = "surface", 
                     colors = "YlOrRd") %>% 
  layout(scene = list(aspectmode = "manual",
                      aspectratio = list(x = 1, 
                                         y = 1, 
                                         z = 1)))
Young.sm.plot
```
```{r}
library(sp)

subset_data %>%
  st_as_sf(coords= c("X Position", "Y Position"))

coords <- data.frame(x = subset_data$`X Position`, y = subset_data$`Y Position`, z = subset_data$`Young's Modulus [Pa]`)

#Create a spatialpointdataframe:
sp_spdf <- SpatialPointsDataFrame(coords = coords[, 1:2],
                                  data = coords[3])

#Empirical variogram
gstat::variogram(z ~ 1, data = sp_spdf) %>%
  fit.variogram(model = vgm("Exp", "Sph", "Gau")) -> variogram

#Build an object that describes all features of the model
model <- gstat(
  formula = z ~ 1,
  locations = sp_spdf,
  model = variogram
    )

xy <- expand.grid(seq(from = -2.6e-5, to = 2.6e-5, by = 1e-6), seq(from = -2.5e-5, to = 2.5e-5, by = 1e-6))
names(xy) <- c("x", "y")
gridded(xy) <- ~ x + y
prediction <- predict(model, newdata = xy, nmax=1)

prediction_df <- as.data.frame(prediction)

ggplot(prediction_df, aes(x = x, y = y, fill = var1.pred)) +
     geom_tile() +
     scale_fill_viridis(option = "YlOrRd", direction = -1) +
     theme_minimal() +
     labs(fill = "Young's Modulus [Pa]",
          x = "X Position",
          y = "Y Position",
          title = "Spatial Prediction of Young's Modulus")


#image(prediction, col = "YlOrRd", asp=1)


```


```{r}
library(viridis)

vc <- variogram(YoungMod ~ 1, data= map.sf, cloud = TRUE)
plot(vc)

v <- variogram(YoungMod ~ 1, data = map.sf)
plot(v)

fv <- fit.variogram(object = v,
                    model = vgm(psill = 40000, model = "Sph",
                                range = 2e-5, nugget = 50))
fv
plot(v, fv, cex = 1.5)
k <- gstat(formula = YoungMod ~ X2 + X + XY + Y + Y2, data = map.sf, model = fv)
kpred <- predict(k, df.sf)

ggplot() + geom_sf(data = kpred, aes(color = var1.pred)) +
  geom_sf(data = map.sf) +
  scale_color_viridis(name = "YoungMod") + theme_bw()

ggplot() + geom_sf(data = kpred, aes(color = var1.var)) +
  geom_sf(data = map.sf) +
  scale_color_viridis(name = "std(YoungMod)") + theme_bw()

Young2.km <- matrix(data = kpred$var1.pred,
               nrow = 50,
               ncol = 50, 
               byrow = TRUE)

Young2.km.plot <- plot_ly(x = ~X.p,
                     y = ~Y.p, 
                     z = ~Youn2g.km, 
                     type = "surface", 
                     colors = "YlOrRd") %>% 
  layout(scene = list(aspectmode = "manual", 
                      aspectratio = list(x = 1,
                                         y = 1,
                                         z = 1)))
Young.km.plot
```
